{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-09-06 wacv_for_review.tex
Figure Updated DeeEnKCF

Since Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high} on VOT15
challenge \footnote{\url{http://www.votchallenge.net/vot2015/}}, many
variation of KCF were investigated. For example, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is similar to that of \cite{ma2015long} in
that more than one KCF is used to address the challenges of single
target tracking. But ours is different from their approach because we
do not use those multiple KCFs together at every frame, but
alternatively at every $k$ frame. It intuitively makes sense to
alternatively use multiple KCFs with different purposes because the
appearance of a target does not change drastically over consecutive
image frames. For most case, even it looks the appearance changes,
learning a correlation filter over consecutive frames would not be
much different from the one learned using the image few or $k$ frames
later. Figure \ref{fig:Filters_Comparison} shows examples supporting
this observation.
\begin{figure}[!h]
\centering
\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
   \\[-3ex]
\subfloat[Small Area Translation Filter]{\hspace{.30\linewidth}}\label{fig:Rt_S}
\quad\subfloat[Large Area Translation Filter]{\hspace{.37\linewidth}}\label{fig:Rt_L}
\quad\quad\subfloat[Scale Filter]{\hspace{.12\linewidth}}\label{fig:Rs}
\caption{Examples of three filters with hand-crafted features; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their Hanning window and
  expected Gaussian response.}
\label{fig:Filters}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
\caption{The proposed conv224-VGGNet feature extraction framework in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
to avoid distortion due to FFT operation whereas $R_{s}$ is not filtered as it would result in target boundary information loss.}
\label{fig:Filters_CNN}
\end{figure}

@@

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at 30fps on a single-board, embedded
system. Given this goal, we used fHoG and color-naming features in an
efficient way in the proposed {\it E}nKCF. Deep features, on the
other hand, recently have been used to boost tracking accuracy of the
KCFs based trackers \cite{ma2015hierarchical,
  danelljan2015convolutional}. Following the recent trend, we hypothesize 
that the {\it E}nKCF tracker could be improved with deep features trained on ImageNet
dataset. Utilizing pre-trained deep features would not be applicable to
all the a single-board, embedded system due to their limited
computational resources. However, as these days some of the single-board
systems offer GPU, we would like to see how much accuracy we can
achieve by feeding {\it E}nKCF w/ deep features (Deep{\it E}nKCF) as shown in Figure \ref{fig:Filters_CNN}.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

@@

Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows experimental
results of utilizing DNN features on UAV123 Dataset. Two settings of utilizing the deep
features outperformed the HoG and color features as proposed in {\it
  E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in
success rates (AUC). The \textit{conv224-VGG} setting performed
slightly better than \textit{conv222-VGG} in precision while achieving
similar success rate (AUC) indicating that higher level feature abstraction
works better for the smaller ROIs.
\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\tiny\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.40cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's ({\it hog} + {\it color}) performance with Deep{\it E}nKCF on the UAV123
dataset.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}

>>>>

Since Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high} on VOT15
challenge \footnote{\url{http://www.votchallenge.net/vot2015/}}, many
variation of KCF were investigated. For example, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is similar to that of \cite{ma2015long} in
that more than one KCF is used to address the challenges of single
target tracking. But ours is different from their approach because we
do not use those multiple KCFs together at every frame, but
alternatively at every $k$ frame. It intuitively makes sense to
alternatively use multiple KCFs with different purposes because the
appearance of a target does not change drastically over consecutive
image frames. For most case, even it looks the appearance changes,
learning a correlation filter over consecutive frames would not be
much different from the one learned using the image few or $k$ frames
later. Figure \ref{fig:Filters_Comparison} shows examples supporting
this observation.
\begin{figure}[!h]
\centering
\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
   \\[-3ex]
\subfloat[Small Area Translation Filter]{\hspace{.30\linewidth}}\label{fig:Rt_S}
\quad\subfloat[Large Area Translation Filter]{\hspace{.37\linewidth}}\label{fig:Rt_L}
\quad\quad\subfloat[Scale Filter]{\hspace{.12\linewidth}}\label{fig:Rs}
\caption{Examples of three filters with hand-crafted features; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their hanning window and
  expected Gaussian response.}
\label{fig:Filters}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
\caption{The proposed conv224-VGGNet feature extraction framework in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied hanning window
to avoid distortion due to FFT operation whereas $R_{s}$ is not filtered as it would result in target boundary information loss.}
\label{fig:Filters_CNN}
\end{figure}

@@

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at 30fps on a single-board, embedded
system. Given this goal, we used fHoG and color-naming features in an
efficient way in the proposed {\it E}nKCF. Deep features, on the
other hand, recently have been used to boost tracking accuracy of the
KCFs based trackers \cite{ma2015hierarchical,
  danelljan2015convolutional}. Following the recent trend, we hypothesize 
that the {\it E}nKCF tracker could be improved with deep features trained on ImageNet
dataset. Utilizing pre-trained deep features would not be applicable to
all the a single-board, embedded system due to their limited
computational resources. However, as these days some of the single-board
systems offer GPU, we would like to see how much accuracy we can
achieve by feeding {\it E}nKCF w/ deep features (Deep{\it E}nKCF) learned by the VGGNet
as shown in Figure \ref{fig:Filters_CNN}.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

@@

Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows experimental
results of utilizing DNN features on UAV123 Dataset. Two settings of utilizing the deep
features outperformed the HoG and color features as proposed in {\it
  E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in
success rates (AUC). The \textit{conv224-VGG} setting performed
slightly better than \textit{conv222-VGG} in precision while achieving
similar success rate (AUC) indicating that higher level feature abstraction
works better for the smaller ROIs.
\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\tiny\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.40cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's ({\it fhog} + {\it color-naming}) performance with Deep{\it E}nKCF on the UAV123
dataset.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}
